% resume.tex
% vim:set ft=tex spell:

\documentclass[9pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Cyril Garcia}}

(408) 440-6918 \ \textbullet
\ \ me@bycyril.com\ \ \textbullet
\ \ ByCyril.com

\ \ twitter.com/\_bycyril \ \textbullet
\ \ github.com/bycyril \ \textbullet
\ \ linkedin.com/in/bycyril
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Apple Inc.}}
		{\textbf{Cupertino, CA}}
	\\
	\headerrow
		{\emph{iOS Software Engineer}}
		{\emph{August 2021 -- Present}}
	\begin{itemize*}
		\item Springboard Multitasking.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{SiriusXM}}
		{\textbf{Oakland, CA}}
	\\
	\headerrow
		{\emph{iOS Software Engineer Intern}}
		{\emph{June 2020 -- August 2020}}
	\begin{itemize*}
		\item Responsible for improving and updating video ad frameworks for iOS.
		\item Enhanced video ad experience with a skip countdown.
		\item Adopted new internal A/B testing framework.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Pandora Media}}
		{\textbf{Oakland, CA}}
	\\
	\headerrow
		{\emph{iOS Software Engineer Intern}}
		{\emph{June 2019 - August 2019}}
	\begin{itemize*}
		\item Responsible for developing and designing a feature to enhance the users ad experience.
		\item Developed various solutions for on-device speech recognition using KeenASR, OpenEars, and SFSpeechRecognizer.
		\item Developed extensive unit tests for ad features.
	\end{itemize*}
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Technical Presentations}

\begin{itemize}
	\parskip=0.1em
	\item
	\headerrow
		{\textbf{Introduction to Deep Learning with TensorFlow}}
		{\textbf{WomenWhoCode - Mobile}}
	\\
	\headerrow
		{A deep dive into the inner workings of a neural network and TensorFlow}
		{\emph{May 2021}}
	\item
	\headerrow
		{\textbf{Swift and Machine Learning}}
		{\textbf{Spring into Swift}}
	\\
	\headerrow
		{Two separate talks on Swift and CoreML}
		{\emph{April 2021}}
	\item
	\headerrow
		{\textbf{A Conversation about iOS Development}}
		{\textbf{Headless \{ Creators \}}}
	\\
	\headerrow
		{Had the opportunity to be a guest speaker on a podcast episode to talk about iOS Development}
		{\emph{October 2020}}
	\item
	\headerrow
		{\textbf{Machine Learning for iOS}}
		{\textbf{Silicon Valley Code Camp}}
	\\
	\headerrow
		{An introductory presentation on Machine Learning for iOS Developers}
		{\emph{September 2019}}
\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Projects}

\begin{itemize}
	\parskip=0.1em
	\item {\textbf{GeekWeather}} \hfill
	{\emph{URLSession, Cocoapods, SwiftUI, Swift, UIKit, Widgets, MVC}}
	\item {\textbf{SOS Board Game}} \hfill
	{\emph{Swift, MVVM, Firebase, AI, Cocoapods, UIKit}}
	\item {\textbf{FileStorks}} \hfill
	{\emph{Swift, Firebase, UIKit, MVC}}
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{San Jose State University}}
		{\textbf{San Jose, CA}}
	\\
	\headerrow
		{\emph{B.S. Statistics}}
		{\emph{May 2021}}
	\item
	\headerrow
		{\textbf{Evergreen Valley College}}
		{\textbf{San Jose, CA}}
	\\
	\headerrow
		{\emph{A.S. Mathematics}}
		{\emph{May 2018}}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Programming Languages:]
	Swift, Objective-C, Javascript, Python
	\item[Frameworks:]
	UIKit, SwiftUI, Vision, CoreML, Foundation, XCTest
	\item[Tools:]
	Xcode, Sketch, Sublime, VS Code
	\item[Interests:]
	iOS Engineering, Programming design and architecture, UI/UX, machine learning theory
\end{description*}
\end{indentsection}

\end{document}
